Follow-up Samples

### 2017-01-25 submission/manuscript_outline_20161024.tex
update with time imporvements

One limitation of our study is that we do not know whether individuals
who were still classified as positive by the lesion model eventually had
a subsequent CRC diagnosis. This information would help to strengthen
the case for our Random Forest based model to have kept a number of
individuals above the cutoff threshold even though at follow up they
were diagnosed as no longer having a lesion. Another limitation is that
we do not know if adding modern tests such as the stool DNA test
{[}20{]} could help improve our overall AUC. Another limitation is that
this study drew heavily from those with caucasian ancestry. The results
may not be immediately representative of those with either Asian or
African ancestry. Finally, although our training and test set are
relatively large we still run the risk of overfitting or having a model
that may not be immediately extrapolateable to other populations. We've
done our best to safeguard against this by not only running 10-fold
cross validation but also having over 100 different 80/20 splits to try
and mimic the type of variation that might be expected to occur.

>>>>

One limitation of our study is that we do not know whether individuals
who were still classified as positive by the lesion model eventually had
a subsequent CRC diagnosis. This information would help to strengthen
the case for our Random Forest based model to have kept a number of
individuals above the cutoff threshold even though at follow up they
were diagnosed as no longer having a lesion. Another limitation is that
we do not know if adding modern tests such as the stool DNA test
{[}20{]} could help improve our overall AUC. Another limitation is that
this study drew heavily from those with caucasian ancestry. The results
may not be immediately representative of those with either Asian or
African ancestry. Finally, although our training and test set are
relatively large we still run the risk of overfitting or having a model
that may not be immediately extrapolateable to other populations. We've
done our best to safeguard against this by not only running 10-fold
cross validation but also having over 100 different 80/20 splits to try
and mimic the type of variation that might be expected to occur. The
time difference in collection of sample between adenoma and carcinoma
that was observed could have affected our observed results. However, our
random forest based model, specifically the lesion trained model, were
still able to adjust positive probabilities for both adenoma and
carcinoma to similar amounts despite this.
